My first RMD file
=================


###1. First, load the data from the current directory.

```{r readata, results="hide"}
mdata<- read.csv("activity.csv")

```


###2. What is mean total number of steps taken per day?

####2.1 Total number steps

```{r calulate total steps , fig.path='figure/' }
mdata1<- mdata[!is.na(mdata$steps),]
dt1<-aggregate(steps ~ date, mdata1, sum)
hist(dt1$steps , xlab = "Total steps" , main = "Histogram fo total steps perday")
```

####2.2 Mean and Median of total number steps

```{r calulate mean steps }
meanTotal<-mean(dt1$steps)
medianTotal<-median(dt1$steps)
```
So the mean of total number of steps taken per day is `r as.character(signif(meanTotal,7))` , the median of total number of steps taken per day is `r medianTotal`.

###3. What is the average daily activity pattern?

####3.1 5-minnute interval steps 
```{r calulate interval average steps, fig.path='figure/' }
dt2<-aggregate(steps ~ interval, mdata1, mean)
plot(dt2,  type = "l")
```

####3.2 which interval has the max average steps
```{r calulate max average steps interval}
max<-dt2[dt2$steps == max(dt2$steps),]
maxsteps<-max$steps
maxstepsInterval<-max$interval
```
So the max average steps is `r maxsteps` of interval `r maxstepsInterval`

###4. Imputing missing values
####4.1 calculate total number of missing values in the dataset 
```{r calulate total missing}
miss <- mdata[is.na(mdata$steps),]
nubmerofRows <- nrow(miss)
```
The number of the rows has missing values is `r nubmerofRows`

####4.2 calculate total number of missing values in the dataset 
```{r add missing values by interval mean,fig.path='figure/'}
mdata2 <- mdata
mdata2[which(is.na(mdata2$steps)),1]<-
         dt2[as.character(mdata2[which(is.na(mdata2$steps)),3]),2]
dt3<-aggregate(steps ~ date, mdata2, sum)
hist(dt3$steps , xlab = "Total steps" , main = "Histogram fo total steps perday(input missing)")

meanTotal2<-mean(dt3$steps)
medianTotal2<-median(dt3$steps)
```
So the mean of total number of steps(input missing) taken per day is `r as.character(signif(meanTotal2,7))` , the median of total number of steps(input missing)  taken per day is `r as.character(signif(medianTotal2,7))`. Both the two values are slightly reduced, because this time we have add days which are missed previously

###5. Are there differences in activity patterns between weekdays and weekends?
```{r add compare weekday weekend,fig.path='figure/'}
dayType <- function(dates) {
  f <- function(date) {
    if (weekdays(as.Date(date)) %in% c("星期六", "星期日")) {
      "weekend"
    }
    else {
      "weekday"
    }
  }
  sapply(dates, f)
}

mdata1$dayType <- as.factor(dayType(mdata1$date))

mdata1_we <- subset(mdata1, dayType == "weekend") 
mdata1_wd <- subset(mdata1, dayType == "weekday") 
daily_we<-aggregate(steps ~ interval, mdata1_we, mean)
daily_wd<-aggregate(steps ~ interval, mdata1_wd, mean)
par(mfrow=c(2,1))
plot(daily_wd, type = "l", main = "Steps on Weekdays")
plot(daily_we, type = "l", main = "Steps on Weekends")
```
